### 2017-10-30 manuscript.rmd
removed bract types analyses and plot

pneuma = cdata$Pneumatophore
names(pneuma) = rownames(cdata)

@@

bracts = cdata$Bract.types
names(bracts) = rownames(cdata)

@@

Stochastic trait mapping:
```{r simmap_making, echo=F, message=F, warning=F}
#Make simmap objects
print("SIMMAP Sex Distribution")
make.simmap(ultratree, sex, nsim = 100, message=FALSE) -> sex_sim
print("SIMMAP Palpons")
make.simmap(ultratree, palpons, nsim = 100, message=FALSE) -> palpons_sim
print("SIMMAP Tentilla")
make.simmap(ultratree, tentilla, nsim = 100, message=FALSE) -> tentilla_sim
print("SIMMAP Tentilla2")
make.simmap(ultratree, tentilla2, nsim = 100, message=FALSE) -> tentilla_sim2
print("SIMMAP Nectosome")
make.simmap(ultratree, nectosome, nsim = 100, message=FALSE) -> nectosome_sim
print("SIMMAP Nectosome Position")
make.simmap(ultratree, necto_pos, nsim = 100, message=FALSE) -> necto_pos_sim
print("SIMMAP Nectophore Types")
make.simmap(ultratree, necto_types, nsim = 100, message=FALSE) -> necto_types_sim
print("SIMMAP Pneumatophore")
make.simmap(ultratree, pneuma, nsim = 100, message=FALSE, pts=T) -> pneuma_sim
print("SIMMAP Bract Types")
make.simmap(ultratree, bracts, nsim = 100, message=FALSE) -> bracts_sim
print("SIMMAP Habitat")
make.simmap(ultratree, vrange, nsim = 100, message=FALSE) -> vrange_sim

@@

SIMMAP Presence of Pneumatophore:
```{r pneumatophore, echo=F, message=F, warning=F, fig.height=7, fig.width=12}
#Simmap PNEUMATOPHORE
plotTree(ultratree, lwd = 4)
colors = c("black", "red")
names(colors) = c("Absent", "Present")
pneuma_sim %>% plotSimmap(lwd = 4, add = T,colors=colors)
nodelabels(pie=(describe.simmap(pneuma_sim, plot=F)$ace) ,piecol=colors,cex=0.35)
add.simmap.legend(colors = colors, x=0.6*par()$usr[1],y=0.3*par()$usr[4],prompt=FALSE)
densityMap(pneuma_sim)
```

@@

SIMMAP Number of Bract types:
```{r bract_types, echo=F, fig.height=7, fig.width=12, message=F, warning=F}
#Simmap bract-types
plotTree(ultratree, lwd = 4)
colors = c("black", "red", "green3", "blue")
names(colors) = c("No bracts", "1", "2", "4")
bracts_sim %>% plotSimmap(lwd = 4, add = T,colors=colors) -> bract_sim_plot
#plot(bract_sim_plot[2])
nodelabels(pie=(describe.simmap(bracts_sim, plot=F)$ace) ,piecol=colors,cex=0.35)
add.simmap.legend(colors = colors, x=0.6*par()$usr[1],y=0.3*par()$usr[4],prompt=FALSE)
```

@@

Continuous traits: Brownian motion reconstructions
Number of bract types reconstruction:
```{r cont_bract_types, echo=F, message=F, warning=F}
contMap(ultratree, bracts)
```
Trait = Number of Bract Types

@@

```{r phylosig_bracts_declare, include=F, echo=F, message=F, warning=F}
physig_bracts_simp = phylosignal(bracts, ultratree)
physig_bracts_mult = physignal(bracts, ultratree)
```
Phylogenetic signal in bract number
```{r phylosig_bracts, echo=F}
physig_bracts_simp
physig_bracts_mult
```

>>>>

@@

@@

Stochastic trait mapping:
```{r simmap_making, echo=F, message=F, warning=F}
#Make simmap objects
print("SIMMAP Sex Distribution")
make.simmap(ultratree, sex, nsim = 100, message=FALSE) -> sex_sim
print("SIMMAP Palpons")
make.simmap(ultratree, palpons, nsim = 100, message=FALSE) -> palpons_sim
print("SIMMAP Tentilla")
make.simmap(ultratree, tentilla, nsim = 100, message=FALSE) -> tentilla_sim
print("SIMMAP Tentilla2")
make.simmap(ultratree, tentilla2, nsim = 100, message=FALSE) -> tentilla_sim2
print("SIMMAP Nectosome")
make.simmap(ultratree, nectosome, nsim = 100, message=FALSE) -> nectosome_sim
print("SIMMAP Nectosome Position")
make.simmap(ultratree, necto_pos, nsim = 100, message=FALSE) -> necto_pos_sim
print("SIMMAP Nectophore Types")
make.simmap(ultratree, necto_types, nsim = 100, message=FALSE) -> necto_types_sim
print("SIMMAP Habitat")
make.simmap(ultratree, vrange, nsim = 100, message=FALSE) -> vrange_sim

@@

@@

@@

Continuous traits: Brownian motion reconstructions

@@

```{r phylosig_bracts_declare, include=F, echo=F, message=F, warning=F}
physig_bracts_simp = phylosignal(bracts, ultratree)
physig_bracts_mult = physignal(bracts, ultratree)
```
